Guarded Recursion in Agda via Sized Types

### 2019-04-18 code-oneclock-paper/latex/Introduction.tex
Minor changes in intro

The decision to restrict the clock context of \GTT\ to contain at 
most one clock variable was dictated by 
our choice to use Agda with sized types as the metatheory. In Agda, 
it is possible to encode semantic clock contexts containing multiple 
clocks as lists of sizes or as functions from a finite interval of 
natural numbers into sizes. But Agda's support for sized types is 
tailored to types depending on exactly one size, or on a finite but 
precise number of sizes, which makes it cumbersome to work with types 
depending on clock contexts containing an indefinite number of clocks. 
More technically, as it was privately communicated to us by Agda 
implementors, Agda's type inference only works properly for 
first-order size contraints. We believe that if future Agda 
releases will add the capability of handling multiple sizes, then it would 
be possible to extend the semantics of \GTT\ to a model for the full 
Atkey and McBride's type theory. We also believe that extending our 
formalization to the multiclock case, while technically challenging, 
will not be conceptually harder. 
\GTT\ is stricly less expressive than Atkey and McBride's calculus, since we are 
unable to implement nested coinductive types. But the one clock 
variant of the calculus still allows the construction of a large 
class of coinductive types and it is the subject of active research
\cite{CloustonBGB15}.

>>>>

The decision to restrict the clock context of \GTT\ to contain at 
most one clock variable was dictated by 
our choice to use Agda with sized types as the metatheory. In Agda, 
it is possible to encode semantic clock contexts containing multiple 
clocks as lists of sizes or as functions from a finite interval of 
natural numbers into sizes. However, Agda's support for sized types is 
tailored to types depending on exactly one size, or on a finite but 
precise number of sizes, which makes it cumbersome to work with types 
depending on clock contexts containing an indefinite number of clocks. 
More technically, as it was privately communicated to us by Agda 
implementors, Agda's type inference only works properly for 
first-order size constraints. We believe that if future Agda 
releases add the capability of handling multiple sizes, it would 
be possible to extend the semantics of \GTT\ to include the full 
Atkey and McBride's type theory. We also believe that extending our 
formalization to the multiclock case, while technically challenging, 
would not be conceptually harder.

\GTT\ is stricly less expressive than Atkey and McBride's calculus, since we are 
unable to implement nested coinductive types. But the one clock 
variant of the calculus still allows the construction of a large 
class of coinductive types and it is the subject of active research
\cite{CloustonBGB15}.
